---
title: "R Notebook"
output: html_notebook
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Introduction

Exploration of the results



```{r}
library(Mcomp)
library(xgboost)
library(mlr)
library(parallel)
library(parallelMap)
library(tidyr)
library(tseries)
#library(Metrics)
library(forecast)
library(EnvStats) #for geometric mean
#library(Metrics) # for MASE
library(ggplot2)
library(smooth)
library(xts)
library(data.table)

```

Loading all the results calculated

```{r}
load("4-steps.RData")
load("12-steps.RData")
load("13-steps.RData")
load("extra_ml.RData")
load("12-steps-extra.RData")
load("4-steps-extra.RData")
load("extra_ets.RData")
```

Removing nulls

```{r}
final_12_is_list <- final_12_is_list[lengths(final_12_is_list) != 0]
final_12_ps_list <- final_12_ps_list[lengths(final_12_ps_list) != 0]
final_12_extra <- final_12_extra[lengths(final_12_is_list) != 0]
final_13_is_list <- final_13_is_list[lengths(final_13_is_list) != 0]
final_13_ps_list <- final_13_ps_list[lengths(final_13_ps_list) != 0]

final_13_extra_ets<-final_13_extra_ets[-c(16,63)]
final_13_extra_ml<-final_13_extra_ml[-c(16,63)]
final_12_extra_ets<- final_12_extra_ets[-56]
final_12_extra_ml<- final_12_extra_ml[-56]
final_4_extra_ets<-final_4_extra_ets[-c(26,75,77)]
final_4_extra_ml<-final_4_extra_ml[-c(26,75,77)]

```

The Results : 


```{r}
x<- final_4_is_list[-c(26,75)]
cols <- colnames(final_4_is_list[[1]])
to_divide <- length(x)
#26 and 75 have a problem
total_4 <- data.frame(Reduce('+', lapply(x, '[', cols)))/to_divide
print.data.frame(total_4)

```

```{r}
x<- final_13_is_list
cols <- colnames(final_13_is_list[[1]])
to_divide <- length(final_13_is_list)
#26 and 75 have a problem
total_13 <- data.frame(Reduce('+', lapply(x, '[', cols)))/to_divide
print.data.frame(total_13)

```

```{r}
x<- final_12_is_list
cols <- colnames(final_12_is_list[[1]])
to_divide <- length(final_12_is_list)
#26 and 75 have a problem
total_12 <- data.frame(Reduce('+', lapply(x, '[', cols)))/to_divide
print.data.frame(total_12)

```

Plotting

1. Quarterly : 

```{r, fig.height=5, fig.width=7}
#Getting the method that produced the best MIS on the simmulation method!
validated <- total_4[-5,] #Without means
#par(bg = 'aliceblue')
plot(c(1:4) , validated$ErrorDirect, type='l', col='red',ylim=c(0.9,1.35) ,pch = 1,
      xlab="Horizon h" , ylab = "GMRAE Interval Scores",lwd=2)
lines(c(1:4) , validated$ErrorKDE , col = 'blue ',lwd=2 ,type='o' ,pch=2)
lines(c(1:4), validated$SimDirect, col = 'yellow',lwd=2 ,type='o',pch=3)
lines(c(1:4), validated$SimKDE, col = 'purple',lwd=2 ,type='o',pch=4)
lines(c(1:4), validated$BootDirect, col = 'green',lwd=2 ,type='o',pch=5)
lines(c(1:4), validated$BootKDE, col = 'black',lwd=2 ,type='o',pch=6)
lines(c(1:4), validated$XGB_Direct, col = 'brown',lwd=2 ,type='o',pch=7)
lines(c(1:4), validated$XGB_KDE, col = 'pink',lwd=2 ,type='o',pch=8)


legend(0.9,1.24, legend = c("ErrorDirect" ,"ErrorKDE","SimDirect", "SimKDE" , "BootDirect", "BootKDE",
                            "XGBDirect" , "XGBKDE")
         ,col=c("red", "blue" , "yellow" , "purple" , "green" , "black" , "brown","pink"),
       lty=1, cex=0.7 , pch=c(1,2,3,4,5,6,7,8)) 

```

2. Weekly:


```{r, fig.height=5, fig.width=7}
#Getting the method that produced the best MIS on the simmulation method!
validated <- total_13[-14,] #Without means
#par(bg = 'aliceblue')
plot(c(1:13) , validated$ErrorDirect, type='l', col='red',ylim=c(0.8,1.3) ,pch = 1,
      xlab="Horizon h" , ylab = "GMRAE Interval Scores",lwd=2)
lines(c(1:13) , validated$ErrorKDE , col = 'blue ',lwd=2 ,type='o' ,pch=2)
lines(c(1:13), validated$SimDirect, col = 'yellow',lwd=2 ,type='o',pch=3)
lines(c(1:13), validated$SimKDE, col = 'purple',lwd=2 ,type='o',pch=4)
lines(c(1:13), validated$BootDirect, col = 'green',lwd=2 ,type='o',pch=5)
lines(c(1:13), validated$BootKDE, col = 'black',lwd=2 ,type='o',pch=6)
lines(c(1:13), validated$XGB_Direct, col = 'brown',lwd=2 ,type='o',pch=7)
lines(c(1:13), validated$XGB_KDE, col = 'pink',lwd=2 ,type='o',pch=8)


legend("topleft", legend = c("ErrorDirect" ,"ErrorKDE","SimDirect", "SimKDE" , "BootDirect", "BootKDE",
                            "XGBDirect" , "XGBKDE")
         ,col=c("red", "blue" , "yellow" , "purple" , "green" , "black" , "brown","pink"),
       lty=1, cex=0.7 , pch=c(1,2,3,4,5,6,7,8)) 

```


3. Monthly

```{r, fig.height=5, fig.width=7}
#Getting the method that produced the best MIS on the simmulation method!
validated <- total_12[-13,] #Without means
#par(bg = 'aliceblue')
plot(c(1:12) , validated$ErrorDirect, type='l', col='red',ylim=c(0.8,1.3) ,pch = 1,
      xlab="Horizon h" , ylab = "GMRAE Interval Scores",lwd=2)
lines(c(1:12) , validated$ErrorKDE , col = 'blue ',lwd=2 ,type='o' ,pch=2)
lines(c(1:12), validated$SimDirect, col = 'yellow',lwd=2 ,type='o',pch=3)
lines(c(1:12), validated$SimKDE, col = 'purple',lwd=2 ,type='o',pch=4)
lines(c(1:12), validated$BootDirect, col = 'green',lwd=2 ,type='o',pch=5)
lines(c(1:12), validated$BootKDE, col = 'black',lwd=2 ,type='o',pch=6)
lines(c(1:12), validated$XGB_Direct, col = 'brown',lwd=2 ,type='o',pch=7)
lines(c(1:12), validated$XGB_KDE, col = 'pink',lwd=2 ,type='o',pch=8)


legend("topleft", legend = c("ErrorDirect" ,"ErrorKDE","SimDirect", "SimKDE" , "BootDirect", "BootKDE",
                            "XGBDirect" , "XGBKDE")
         ,col=c("red", "blue" , "yellow" , "purple" , "green" , "black" , "brown","pink"),
       lty=1, cex=0.7 , pch=c(1,2,3,4,5,6,7,8)) 



```










EMP_mat,KDE_mat,SimDirectEMP_mat,SimMeanSigma_mat,SimMeanEMP_mat,SimMeanKDE_mat,BootDirectEMP_mat,

BootMeanSigma_mat,BootMeanKDE_mat,Alg_mat,test_mat,point_mat
```{r}

final_12_extra_ets_final <- list()
final_12_extra_ets_final_ps <- list()
#Getting GMRAE
for (i in 1:length(final_12_extra_ets)){
  final_12_extra_ets_final[[i]] <- list()
  #final_12_extra_ets_final_ps[[i]] <- list()
  for (j in 1:(length(final_12_extra_ets[[i]])-3)){
    final_12_extra_ets_final[[i]][[j]] <- matrix(NA,dim(final_12_extra_ets[[1]][[1]])[1],dim(final_12_extra_ets[[1]][[1]])[2])
        final_12_extra_ets_final_ps[[i]] <- matrix(NA,dim(final_12_extra_ets[[1]][[1]])[1],dim(final_12_extra_ets[[1]][[1]])[2])
    
    for (z in 1:12){
      
      final_12_extra_ets_final[[i]][[j]][,z] <- abs(final_12_extra_ets[[i]][[j]][,z]/final_12_extra_ets[[i]][[10]][,z])
      #MAPE
      final_12_extra_ets_final_ps[[i]][,z] <- abs((final_12_extra_ets[[i]][[12]][,z]-final_12_extra_ets[[i]][[11]][,z])/final_12_extra_ets[[i]][[11]][,z])
    }
  }
  
}

```



## Exploring the correlation


All sets will be combined and the correlation between Intervals and Points Forecasts for each set of monthly, quarterly and weekly series will be explored.


Combining all sets
```{r}

corr_12 <- final_12_extra_ets_final[[1]]
corr_12_ps <- final_12_extra_ets_final_ps[[1]]
for (i in 2:length(final_12_extra_ets_final)){
  corr_12_ps <- rbind(corr_12_ps,final_12_extra_ets_final_ps[[i]])
  for (j in 1:length(final_12_extra_ets_final[[i]])){
    corr_12[[j]]<-rbind(corr_12[[j]],final_12_extra_ets_final[[i]][[j]])
    
  }
}

```

For monthly series:

On ETS

```{r}
#calculate means
final_12_extra_ets_errors<- list()
#Getting GMRAE
for (i in 1:length(final_12_extra_ets)){

  for (j in 1:(length(final_12_extra_ets[[i]])-3)){
    final_12_extra_ets_errors[[i]] <- matrix(NA,dim(final_12_extra_ets[[1]][[1]])[1],dim(final_12_extra_ets[[1]][[1]])[2])
    
    for (z in 1:12){
      
      #MAPE
      final_12_extra_ets_errors[[i]][,z] <- abs(final_12_extra_ets[[i]][[12]][,z]-final_12_extra_ets[[i]][[11]][,z])
    }
  }
  
}
all_means <- list()
all_means_ps <-list()
for (i in 1:length(final_12_extra_ets)){
  all_means[[i]]<-list()
  for (j in 1:length(final_12_extra_ets_final[[i]])){
    all_means[[i]][[j]] <- colMeans(final_12_extra_ets[[i]][[j]])
    all_means_ps[[i]] <- colMeans(final_12_extra_ets_errors[[i]])
  }
}
#add to a single df for every method
corr_12 <- all_means[[1]]
corr_12_ps <- all_means_ps[[1]]
for (i in 2:length(all_means)){
  corr_12_ps <- rbind(corr_12_ps,all_means_ps[[i]])
  for (j in 1:length(all_means[[i]])){
    corr_12[[j]]<-rbind(corr_12[[j]],all_means[[i]][[j]])
    
  }
}
#make single collumn
corr_12_final <- list()
correl<-list()
corr_12_final_ps <- data.frame(point = c(t(corr_12_ps)), stringsAsFactors=FALSE)
for (i in 1:9){
  corr_12_final[[i]] <- data.frame(interval = c(t(corr_12[[i]])), stringsAsFactors=FALSE)
  correl[[i]] <- cbind(corr_12_final[[i]],corr_12_final_ps)
}
#combining methods
all_12_ets <- correl[[1]]
for (i in 2:length(correl)){
  all_12_ets <- rbind(all_12_ets,correl[[i]])
}

```


For XGBoost

```{r}
#calculate means
#final_12_extra_xgb<- final_12_extra_xgb[-56]
final_12_extra_xgb_errors<- list()
#Getting GMRAE
for (i in 1:length(final_12_extra_xgb)){
  #print(i)
  for (j in 1:(length(final_12_extra_xgb[[i]])-3)){
    final_12_extra_xgb_errors[[i]] <- matrix(NA,dim(final_12_extra_xgb[[1]][[1]])[1],dim(final_12_extra_xgb[[1]][[1]])[2])
    
    for (z in 1:12){
      
      #MAPE
      final_12_extra_xgb_errors[[i]][,z] <- abs(final_12_extra_xgb[[i]][[5]][,z]-final_12_extra_xgb[[i]][[4]][,z])
    }
  }
  
}
all_means <- list()
all_means_ps <-list()
for (i in 1:length(final_12_extra_xgb)){
  all_means[[i]]<-list()
  for (j in 1:length(final_12_extra_xgb[[i]])){
    all_means[[i]][[j]] <- colMeans(final_12_extra_xgb[[i]][[j]])
    all_means_ps[[i]] <- colMeans(final_12_extra_xgb_errors[[i]])
  }
}
#add to a single df for every method
corr_12 <- all_means[[1]]
corr_12_ps <- all_means_ps[[1]]
for (i in 2:length(all_means)){
  corr_12_ps <- rbind(corr_12_ps,all_means_ps[[i]])
  for (j in 1:length(all_means[[i]])){
    corr_12[[j]]<-rbind(corr_12[[j]],all_means[[i]][[j]])
    
  }
}
#make single collumn
corr_12_final <- list()
correl<-list()
corr_12_final_ps <- data.frame(point = c(t(corr_12_ps)), stringsAsFactors=FALSE)
for (i in 1:3){
  corr_12_final[[i]] <- data.frame(interval = c(t(corr_12[[i]])), stringsAsFactors=FALSE)
  correl[[i]] <- cbind(corr_12_final[[i]],corr_12_final_ps)
}
#combining methods
all_12_xgb <- correl[[1]]
for (i in 2:length(correl)){
  all_12_xgb <- rbind(all_12_xgb,correl[[i]])
}

```


For quartely series:

For the ETS:

```{r}
#calculate means
final_4_extra_ets_errors<- list()
#Getting GMRAE
for (i in 1:length(final_4_extra_ets)){

  for (j in 1:(length(final_4_extra_ets[[i]])-3)){
    final_4_extra_ets_errors[[i]] <- matrix(NA,dim(final_4_extra_ets[[1]][[1]])[1],dim(final_4_extra_ets[[1]][[1]])[2])
    
    for (z in 1:4){
      
      #MAPE
      final_4_extra_ets_errors[[i]][,z] <- abs(final_4_extra_ets[[i]][[12]][,z]-final_4_extra_ets[[i]][[11]][,z])
    }
  }
  
}
all_means <- list()
all_means_ps <-list()
for (i in 1:length(final_4_extra_ets)){
  all_means[[i]]<-list()
  for (j in 1:length(final_4_extra_ets[[i]])){
    all_means[[i]][[j]] <- colMeans(final_4_extra_ets[[i]][[j]])
    all_means_ps[[i]] <- colMeans(final_4_extra_ets_errors[[i]])
  }
}
#add to a single df for every method
corr_4 <- all_means[[1]]
corr_4_ps <- all_means_ps[[1]]
for (i in 2:length(all_means)){
  corr_4_ps <- rbind(corr_4_ps,all_means_ps[[i]])
  for (j in 1:length(all_means[[i]])){
    corr_4[[j]]<-rbind(corr_4[[j]],all_means[[i]][[j]])
    
  }
}
#make single collumn
corr_4_final <- list()
correl<-list()
corr_4_final_ps <- data.frame(point = c(t(corr_4_ps)), stringsAsFactors=FALSE)
for (i in 1:9){
  corr_4_final[[i]] <- data.frame(interval = c(t(corr_4[[i]])), stringsAsFactors=FALSE)
  correl[[i]] <- cbind(corr_4_final[[i]],corr_4_final_ps)
}
#combining methods
all_4_ets <- correl[[1]]
for (i in 2:length(correl)){
  all_4_ets <- rbind(all_4_ets,correl[[i]])
}
```

For XGBoost : 

```{r}
#calculate means
#final_4_extra_xgb<-final_4_extra_xgb[-77]
final_4_extra_xgb_errors<- list()
#Getting GMRAE
for (i in 1:length(final_4_extra_xgb)){
  #print(i)
  for (j in 1:(length(final_4_extra_xgb[[i]])-3)){
    final_4_extra_xgb_errors[[i]] <- matrix(NA,dim(final_4_extra_xgb[[1]][[1]])[1],dim(final_4_extra_xgb[[1]][[1]])[2])
    
    for (z in 1:4){
      
      #MAPE
      final_4_extra_xgb_errors[[i]][,z] <- abs(final_4_extra_xgb[[i]][[5]][,z]-final_4_extra_xgb[[i]][[4]][,z])
    }
  }
  
}
all_means <- list()
all_means_ps <-list()
for (i in 1:length(final_4_extra_xgb)){
  all_means[[i]]<-list()
  for (j in 1:length(final_4_extra_xgb[[i]])){
    all_means[[i]][[j]] <- colMeans(final_4_extra_xgb[[i]][[j]])
    all_means_ps[[i]] <- colMeans(final_4_extra_xgb_errors[[i]])
  }
}
#add to a single df for every method
corr_4 <- all_means[[1]]
corr_4_ps <- all_means_ps[[1]]
for (i in 2:length(all_means)){
  corr_4_ps <- rbind(corr_4_ps,all_means_ps[[i]])
  for (j in 1:length(all_means[[i]])){
    corr_4[[j]]<-rbind(corr_4[[j]],all_means[[i]][[j]])
    
  }
}
#make single collumn
corr_4_final <- list()
correl<-list()
corr_4_final_ps <- data.frame(point = c(t(corr_4_ps)), stringsAsFactors=FALSE)
for (i in 1:3){
  corr_4_final[[i]] <- data.frame(interval = c(t(corr_4[[i]])), stringsAsFactors=FALSE)
  correl[[i]] <- cbind(corr_4_final[[i]],corr_4_final_ps)
}
#combining methods
all_4_xgb <- correl[[1]]
for (i in 2:length(correl)){
  all_4_xgb <- rbind(all_4_xgb,correl[[i]])
}

```


Combining ETS and XGBoost scores for every set:

Monthly:

```{r}
all_12 <- rbind(all_12_ets,all_12_xgb)
x <- all_12$interval
y<- all_12$point
#y <- zv2
dim(y) <- c(length(y),1)
#x <- MAM_means
dim(x) <- c(length(x),1)
df_plot <-data.frame(x,y)
ww <- summary(lm(y ~ I(x^1)+ I(x^2) + I(x^3), data = df_plot))
p_val <- toString(ww$coefficients[2,4])
rr <- cor.test(x,y,method="spearman")
yi <- lm(y  ~ I(x^1)+ I(x^2) + I(x^3), data = df_plot)$fitted.values[order(x)]
xi <- sort(x)


plot(x , y, main = "Monthly Interval Scores and Point Errors" ,xlim=c(50,2000) ,ylim = c(5,350), ylab = "Absolute Error", xlab =  "Interval Score" 
     , pch = 19 , col=rgb(0,0,0, alpha=0.15) ,cex = 0.5)
lines(xi,yi, col = "red" , lwd = 2)

```


Quartely:

```{r}
all_4 <- rbind(all_4_ets,all_4_xgb)
all1_4 <- all_4[ which(all_4$point < 3000 &all_4$interval <7000), ]
x <- all1_4$interval
y<- all1_4$point
#y <- zv2
dim(y) <- c(length(y),1)
#x <- MAM_means
dim(x) <- c(length(x),1)
df_plot <-data.frame(x,y)
ww <- summary(lm(y ~ I(x^1)+ I(x^2) + I(x^3), data = df_plot))
p_val <- toString(ww$coefficients[2,4])
rr <- cor.test(x,y,method="spearman")
yi <- lm(y  ~ I(x^1)+ I(x^2) + I(x^3), data = df_plot)$fitted.values[order(x)]
xi <- sort(x)


plot(x , y, main = "Quarterly Interval Scores and Point Errors" ,xlim=c(50,2000) ,ylim = c(5,350), ylab = "Absolute Error", xlab =  "Interval Score" 
     , pch = 19 , col=rgb(0,0,0, alpha=0.25) ,cex = 0.6)
lines(xi,yi, col = "red" , lwd = 2)

```

Finaly for the Weekly Series : 


```{r}
final_13_extra_ets_errors<- list()
#Getting GMRAE
for (i in 1:length(final_13_extra_ets)){

  for (j in 1:(length(final_13_extra_ets[[i]])-3)){
    final_13_extra_ets_errors[[i]] <- matrix(NA,dim(final_13_extra_ets[[1]][[1]])[1],dim(final_13_extra_ets[[1]][[1]])[2])
    
    for (z in 1:13){
      
      #MAPE
      final_13_extra_ets_errors[[i]][,z] <- abs(final_13_extra_ets[[i]][[12]][,z]-final_13_extra_ets[[i]][[11]][,z])
    }
  }
  
}
all_means <- list()
all_means_ps <-list()
for (i in 1:length(final_13_extra_ets)){
  all_means[[i]]<-list()
  for (j in 1:length(final_13_extra_ets[[i]])){
    all_means[[i]][[j]] <- colMeans(final_13_extra_ets[[i]][[j]])
    all_means_ps[[i]] <- colMeans(final_13_extra_ets_errors[[i]])
  }
}
#add to a single df for every method
corr_13 <- all_means[[1]]
corr_13_ps <- all_means_ps[[1]]
for (i in 2:length(all_means)){
  corr_13_ps <- rbind(corr_13_ps,all_means_ps[[i]])
  for (j in 1:length(all_means[[i]])){
    corr_13[[j]]<-rbind(corr_13[[j]],all_means[[i]][[j]])
    
  }
}
#make single collumn
corr_13_final <- list()
correl<-list()
corr_13_final_ps <- data.frame(point = c(t(corr_13_ps)), stringsAsFactors=FALSE)
for (i in 1:9){
  corr_13_final[[i]] <- data.frame(interval = c(t(corr_13[[i]])), stringsAsFactors=FALSE)
  correl[[i]] <- cbind(corr_13_final[[i]],corr_13_final_ps)
}
#combining methods
all_13_ets <- correl[[1]]
for (i in 2:length(correl)){
  all_13_ets <- rbind(all_13_ets,correl[[i]])
}
final_13_extra_xgb_errors<- list()
#Getting GMRAE
final_13_extra_xgb <- final_13_extra_xgb[lengths(final_13_extra_xgb) != 0]
for (i in 1:length(final_13_extra_xgb)){
  #print(i)
  for (j in 1:(length(final_13_extra_xgb[[i]])-3)){
    final_13_extra_xgb_errors[[i]] <- matrix(NA,dim(final_13_extra_xgb[[1]][[1]])[1],dim(final_13_extra_xgb[[1]][[1]])[2])
    
    for (z in 1:4){
      
      #MAPE
      final_13_extra_xgb_errors[[i]][,z] <- abs(final_13_extra_xgb[[i]][[5]][,z]-final_13_extra_xgb[[i]][[4]][,z])
    }
  }
  
}
all_means <- list()
all_means_ps <-list()
for (i in 1:length(final_13_extra_xgb)){
  all_means[[i]]<-list()
  for (j in 1:length(final_13_extra_xgb[[i]])){
    all_means[[i]][[j]] <- colMeans(final_13_extra_xgb[[i]][[j]])
    all_means_ps[[i]] <- colMeans(final_13_extra_xgb_errors[[i]])
  }
}
#add to a single df for every method
corr_13 <- all_means[[1]]
corr_13_ps <- all_means_ps[[1]]
for (i in 2:length(all_means)){
  corr_13_ps <- rbind(corr_13_ps,all_means_ps[[i]])
  for (j in 1:length(all_means[[i]])){
    corr_13[[j]]<-rbind(corr_13[[j]],all_means[[i]][[j]])
    
  }
}
#make single collumn
corr_13_final <- list()
correl<-list()
corr_13_final_ps <- data.frame(point = c(t(corr_13_ps)), stringsAsFactors=FALSE)
for (i in 1:3){
  corr_13_final[[i]] <- data.frame(interval = c(t(corr_13[[i]])), stringsAsFactors=FALSE)
  correl[[i]] <- cbind(corr_13_final[[i]],corr_13_final_ps)
}
#combining methods
all_13_xgb <- correl[[1]]
for (i in 2:length(correl)){
  all_13_xgb <- rbind(all_13_xgb,correl[[i]])
}


```

```{r}
all_13 <- rbind(all_13_ets,all_13_xgb)
all1_13 <- all_13[ which(all_13$point < 3000 &all_13$interval <7000), ]
x <- all1_13$interval
y<- all1_13$point
#y <- zv2
dim(y) <- c(length(y),1)
#x <- MAM_means
dim(x) <- c(length(x),1)
df_plot <-data.frame(x,y)
ww <- summary(lm(y ~ I(x^1)+ I(x^2) + I(x^3), data = df_plot))
p_val <- toString(ww$coefficients[2,4])
rr <- cor.test(x,y,method="spearman")
yi <- lm(y  ~ I(x^1)+ I(x^2) + I(x^3), data = df_plot)$fitted.values[order(x)]
xi <- sort(x)


plot(x , y, main = "Quarterly Interval Scores and Point Errors" ,xlim=c(50,2000) ,ylim = c(5,350), ylab = "Absolute Error", xlab =  "Interval Score" 
     , pch = 19 , col=rgb(0,0,0, alpha=0.25) ,cex = 0.6)
lines(xi,yi, col = "red" , lwd = 2)

```

